---
title: "Lab 11"
author: "Skyler Moomey"
date: "11/11/2020"
output: 
  html_document:
    df_print: paged
    fig_caption: true
    highlights: pygments
    number_sections: no
    theme: spacelab
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Tasks 

## Task 1

```{r}
getwd()
```

## Task 2 

### R as Calculator, Mean

```{r}
d=c(5.0581, 4.9707, 5.0893, 4.9334, 4.9777, 5.0285, 4.8555, 4.9565, 
4.9769, 4.9722, 4.999, 4.9925, 4.9686, 5.0662, 4.9239, 4.9781, 
5.0485, 5.0014, 4.9957, 5.0195, 5.0118, 4.9928, 5.0361, 5.0185, 
4.9879)

##0.95 confidence interval
print("95% confidence")
t=qt(0.975,length(d)-1)
ci=c()
ci[1]=mean(d)-t*sd(d)/sqrt(length(d))
ci[2]=mean(d)+t*sd(d)/sqrt(length(d))
ci

##0.90 confidence interval
print("90% confidence")
t=qt(0.95, length(d)-1)
ci[1]=mean(d)-t*sd(d)/sqrt(length(d))
ci[2]=mean(d)+t*sd(d)/sqrt(length(d))

ci

##0.80 confidence interval
print("80% confidence")
t=qt(0.90, length(d)-1)
ci[1]=mean(d)-t*sd(d)/sqrt(length(d))
ci[2]=mean(d)+t*sd(d)/sqrt(length(d))

ci

##0.50 confidence interval
print("50% confidence")
t=qt(0.75, length(d)-1)
ci[1]=mean(d)-t*sd(d)/sqrt(length(d))
ci[2]=mean(d)+t*sd(d)/sqrt(length(d))

ci


```

### T-Test, mean

```{r}
##80% confidence interval using t.test
print("T-Test:")
interval = t.test(d, conf.level=0.80)$conf.int
interval
```


### R as Calculator, Variance

```{r}

## .95 confidence interval
chis1=qchisq(0.975, length(d)-1)
chis2=qchisq(0.025, length(d)-1)

ci[1] = ((length(d)-1)*var(d))/(chis1)
ci[2] = ((length(d)-1)*var(d))/(chis2)

ci

## .90 confidence interval
chis1 = qchisq(0.95, length(d)-1)
chis2 = qchisq(0.05, length(d)-1)

ci[1] = ((length(d)-1)*var(d))/(chis1)
ci[2] = ((length(d)-1)*var(d))/(chis2)

ci

##.80 confidence interval
chis1 = qchisq(0.90, length(d)-1)
chis2 = qchisq(0.10, length(d)-1)

ci[1] = ((length(d)-1)*var(d))/(chis1)
ci[2] = ((length(d)-1)*var(d))/(chis2)

ci

## .50 confidence interval
chis1 = qchisq(0.75, length(d)-1)
chis2 = qchisq(0.25, length(d)-1)

ci[1] = ((length(d)-1)*var(d))/(chis1)
ci[2] = ((length(d)-1)*var(d))/(chis2)

ci
```

## Task 3 

### Two Independent Samples, Difference of Means, 95% Confidence Interval

```{r}
blue=c(21.65, 17.48, 20.1, 21.57, 14.82, 19.17, 21.08, 18.23, 22.93, 
15.66, 20.89, 21.66, 18.5, 20.59, 18.63, 18.91, 19.53, 17.7, 16.5, 19.03)

snapper=c(31.65, 27.48, 30.1, 31.57, 24.82, 29.17, 31.08, 28.23, 32.93, 
25.66, 30.89, 31.66, 28.5, 30.59, 28.63)

sp=(((length(blue)-1)*(var(blue)))+((length(snapper)-1)*(var(snapper))))/(length(blue)+length(snapper)-2)

alpha=0.05
t=qt(1-(alpha/2), length(blue)+length(snapper)-2)

ci[1] = mean(blue) - mean(snapper) - t*sqrt(sp*(1/length(blue)+1/length(snapper)))
ci[2] = mean(blue) - mean(snapper) + t*sqrt(sp*(1/length(blue)+1/length(snapper)))

print("Blue - Snapper")
ci

ci[1] = mean(snapper) - mean(blue) - t*sqrt(sp*(1/length(blue)+1/length(snapper)))
ci[2] = mean(snapper) - mean(blue) + t*sqrt(sp*(1/length(blue)+1/length(snapper)))

print("Snapper - Blue")
ci
```

This interval ensures that there's a 95% chance of the difference in means being between $(|8.3571|, |12.2413|)$.

### Two Independent Samples, Difference of Means, Various T-Tests

```{r}
##.95
print("T-Test, conf.level=.95")
t.test(blue, snapper, var.equal=TRUE, conf.level=.95)$conf.int

print("T-Test, conf.level=.85")
t.test(blue, snapper, var.equal=TRUE, conf.level=.85)$conf.int

print("T-Test, conf.level=.75")
t.test(blue, snapper, var.equal=TRUE, conf.level=.75)$conf.int

print("T-Test, conf.level=.25")
t.test(blue, snapper, var.equal=TRUE, conf.level=.25)$conf.int
```

As the confidence level decreases, the range of the confidence interval gets much smaller.

## Task 4